%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
\label{sec:conclusion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Synoptic is a tool for turning complex executions logs into convenient summary models
for analyzing systems. It infers these models by capturing key temporal
properties of the input logs. InvariMint
implements a new model inference engine for constructing similar models. The
InvariMint technique uses a formal languages perspective to express log
invariants which offers improvements over Synoptic's refinement and coarsening
algorithms:

(1) Turning logs into models offers an easy-to-create and easy-to-use
way to analyze systems. By using familiar DFA operations to infer these models,
the InvariMint process is easy for users to understand.

(2) InvariMint is more scalable than Synoptic. The InvariMint model inference technique
refers to the input traces once which makes the DFA intersection and minimization
operations more efficient than refinement and coarsening.

(3) Whereas Synoptic generates models non-deterministically, InvariMint is both
deterministic and captures all possible behaviors allowed by Synoptic models.

Additionally the formal language perspective is extensible: InvariMint makes it trivial to model
any system behavior that can be expressed as a finite state machine. This
generic approach allows InvariMint to be compatible with other inference
techniques, and we believe that it is a unifying framework for generalizing,
combining, and comparing those existing methods.
